Modelling the emergence of whisker barrels

### 2020-07-13 paper/briefpaper/brief.tex
Removes contours from image and changes movie script to generate frames without contours

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{The emergence of whisker barrels.
      %
      \textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}.
      %
      \textbf{B} The strengths of interaction $\gamma$ with fields $\rho_1$
      and $\rho_2$ are indicated for each of 41 projections by the lengths of
      green and blue arrows respectively, assuming that similar fields aligned
      to the posterior-anterior and medial-lateral axes in the ventroposterior
      medial nucleus of the thalamus are sampled at the locations of putative
      barreloid centers (reconstructed from \citealp{haidarliu_size_2001},
      their \MPone{Fig.\,5b}).
      %
      \textbf{C} Results for the example simulation, with parameters
      \MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$,
        $\gamma\in\pm 2$, $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours
      indicate the thalamic projection for which the connection density is
      maximal and black lines delineate boundaries (see Movie S1).
      %
      \textbf{D} Red dots show the \emph{Honda}--\metrics{$\delta(t)$} metric
      obtained from \metrics{the} simulation approaching that obtained from
      the \metrics{real} barrels in \textbf{A} (dotted line); black squares
      show the \emph{pattern difference} metric $\eta(t)$, and reveal the
      emergence of a correspondence between the real and simulated barrel
      shapes (units mm$^3$); \metrics{grey hexagons show how selectively each
        cortical site is innervated;
        $\omega(t) = \oiint_{S} \mu(\mb{x},t) \mathrm{d}S$, where
        $\mu(\mb{x}) \equiv \mathrm{max}_i\big(c_i(\mb{x},t)\big)\big/\sum_{j=1}^{N} c_j(\mb{x},t)$.}
      %
      \textbf{E} \metrics{Plotted across the cortical sheet, the selectivity
        develops to reveal an alignment with the emergent barrel boundary
        shapes}. \metrics{Greyscale colour indicates values of $\mu(\mb{x})$
        and overlaid contours show $c_i > 0.95
        \mathrm{max}_i\big(c_i(\mb{x})\big)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
\MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$}. Colours indicate the thalamic
projection for which the connection density is maximal, black lines delineate
boundaries, and overlaid contours show
\cmnt{$c_i > 0.95 \mathrm{max}_i\big(c_i(\mb{x})\big)$. Barrel labels are
  always located at the centroid of their field(s).} The final frame in the movie
is step 30000 of the simulation.

>>>>

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{The emergence of whisker barrels.
      %
      \textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}.
      %
      \textbf{B} The strengths of interaction $\gamma$ with fields $\rho_1$
      and $\rho_2$ are indicated for each of 41 projections by the lengths of
      green and blue arrows respectively, assuming that similar fields aligned
      to the posterior-anterior and medial-lateral axes in the ventroposterior
      medial nucleus of the thalamus are sampled at the locations of putative
      barreloid centers (reconstructed from \citealp{haidarliu_size_2001},
      their \MPone{Fig.\,5b}).
      %
      \textbf{C} Results for the example simulation, with parameters
      \MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$,
        $\gamma\in\pm 2$, $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours
      indicate the thalamic projection for which the connection density is
      maximal, \cmnt{barrel labels are located at the centroid of each
        region and} black lines delineate boundaries (see Movie S1).
      %
      \textbf{D} Red dots show the \emph{Honda}--\metrics{$\delta(t)$} metric
      obtained from \metrics{the} simulation approaching that obtained from
      the \metrics{real} barrels in \textbf{A} (dotted line); black squares
      show the \emph{pattern difference} metric $\eta(t)$, and reveal the
      emergence of a correspondence between the real and simulated barrel
      shapes (units mm$^3$); \metrics{grey hexagons show how selectively each
        cortical site is innervated;
        $\omega(t) = \oiint_{S} \mu(\mb{x},t) \mathrm{d}S$, where
        $\mu(\mb{x}) \equiv \mathrm{max}_i\big(c_i(\mb{x},t)\big)\big/\sum_{j=1}^{N} c_j(\mb{x},t)$.}
      %
      \textbf{E} \metrics{Plotted across the cortical sheet, the selectivity
        develops to reveal an alignment with the emergent barrel boundary
        shapes}. \metrics{Greyscale colour indicates values of $\mu(\mb{x})$.}
      All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
\MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$}. Colours indicate the thalamic
projection for which the connection density is maximal and black lines delineate
boundaries. \MPtwo{Barrel labels are
  always located at the centroid of their field(s).} The final frame in the movie
is step 30000 of the simulation.
